---
title: "Anticholinergic Meta analysis"
output: 
  html_document:
    keep_md: true
---

### Load packages
```{r setup, results = 'hide', message = FALSE, warning =FALSE}
library(meta)
library(metafor)
library(tidyverse)
```

___

### Data import
Import data (.csv) and assign to `dat`
```{r data import, results = 'hide', warning = FALSE, message = FALSE}
library(readr)
Anticholinergic_Medication_R_data <- read_csv("Z:/PROJECTS/2018_Anticholinergic_Med_SR/Analysis/Final analysis/anticholinergic_med_metaanalysis/dat_antichol.csv")
```

Assign data to `dat`
```{r assign dat}
dat <- Anticholinergic_Medication_R_data %>%
  filter(!is.na(study)) #a blank row keeps being added in the .csv file. This removes it
```

____

### Meta-analysis
#### Step 1: Average across studies
This step is necessary to ensure independence of each effect size entered into the meta-analysis. In the current form, most studies report multiple outcomes (time-points, medication, cognitive tests), and these results are dependent on each other, as they come from they come from the same, or overlapping samples of participants. 

Data are averaged **within studies** so that each study represents a single effect size.
In all cases of studies which included outcomes for different medications, all medications were either low or high potency, so outcomes were able to be averaged together (within the study).

Averaged results are assigned to `dat_study`

```{r study average}
dat_study <- dat %>%
  group_by(study) %>% #group by study so further calculations are done within each study
  mutate(g = mean(g, na.rm = T),
          st_err = mean(st_err, na.rm = T)) %>% #obtain average g and st err within each study, removing NAs from calculation
  filter(row_number()==1) %>% #make each study only appear on one row
  select(study, author, year, potency, g, st_err) #select relevant data for analysis
```

___

#### Step 2: Run random effects model of all data

* Using the Paule-Mandel method

```{r meta whole mod1, results = 'hide'}
meta_all_mod1 <- metagen(g,
                    st_err,
                    data = dat_study,
                    studlab = paste(author, year),
                    comb.fixed = F,
                    comb.random = T,
                    hakn = T,
                    method.tau = "PM", #use Paule-Mandel method
                    sm = "SMD") #calculate SMD
```

Code for forest plot:
```{r meta forest whole mod1, fig.width=8, fig.height=12, results = 'hide', warning = FALSE, message = FALSE}
tiff(file='fig2_meta_forest_whole.tiff', width = 7, height = 10.75, units = "in", res = 600, compression = "lzw")
meta::forest(meta_all_mod1,
             sortvar = TE, #sort by effect size
             xlim = c(-1.5, 1.5),
             leftcols = "studlab",
             rightlabs = c("Hedges' g", "95% CI", "Weight"),
             text.random = "Overall effect",
             overall = TRUE,
             smlab = "",
             weight = FALSE,
             text.overall.random = TRUE,
             overall.hetstat = FALSE)
dev.off()
```

___

#### Step 3: Run subgroup analyses
##### *Potency (low/high)*
Run sub-analyses by medication potency (low/high) for each model.

```{r meta potency subanalysis}
potency_subgroup_mod1 <- update.meta(meta_all_mod1, 
                             byvar=potency, 
                             comb.random = TRUE, 
                             comb.fixed = FALSE)
```

Code for forest plot:
```{r meta forest potency mod1, fig.width = 8, fig.height = 13, results = 'hide', warning = FALSE, message = FALSE}
tiff(file='fig4_meta_forest_potency.tiff', width = 6, height = 11.2, units = "in", res = 600, compression = "lzw")
meta::forest(potency_subgroup_mod1,
             sortvar = TE, #sort by effect size
             xlim = c(-1.5, 1.5),
             leftcols = "studlab",
             rightlabs = c("Hedges' g", "95% CI"),
             text.random = "Overall effect",
             text.overall.random = TRUE,
             overall.hetstat = FALSE,
             print.byvar = F, #this removed "potency =" and just left subgroup label
             smlab = "",
             hetstat = FALSE,
             test.overall = F,
             overall = F,
             prediction = F)
dev.off()
```

___

##### *Cognitive domain*

Create data set (`dat_study_domain`) which has the average effect size by cognitive domain within each study.

Cognitive domains were defined using domains outlined by Lezak (2012): 

* Memory
* Executive function
* Attention
* Psychomotor functioning
* Concept formation & reasoning
* Language
* Intelligence
* Perception

Effect sizes based on cognitive composite scores (reported in 3 studies: Stevenson, Robles, Operto) were not included in the cognitive domain sub analysis. 

```{r domain average}
dat_study_domain <- dat %>%
  group_by(study, cog_domain_lezak) %>% #group by study and cognitive domains (based on Lezak) within studies
  mutate(g = mean(g, na.rm = T),
         st_err = mean(st_err, na.rm = T)) %>% #obtain average g and st err within each study/domain
  filter(row_number()==1) %>% #make each study/domain only appear on one row
  filter(cog_domain_lezak != "Not Subdomain") %>% #remove outcomes based on cognitive composite scores
  select(study, author, year, potency, cog_domain_lezak, g, st_err) #select relevant data
```

Then, run random effects model by subgroup (cognitive domain):

* Use the Paule-Mandel method to estimate tau

```{r meta domain mod1, results = 'hide'}
meta_domain_mod1 <- metagen(g,
                    st_err,
                    data = dat_study_domain,
                    studlab = paste(author, year),
                    comb.fixed = F,
                    hakn = T,
                    comb.random = T,
                    method.tau = "PM", #use Paule-Mandel method
                    sm = "SMD") # says we want to calculate SMD
domain_subgroup_mod1 <- update.meta(meta_domain_mod1, 
                                byvar=cog_domain_lezak, 
                                comb.random = TRUE, 
                                comb.fixed = FALSE)
```

Code for forest plot:
```{r meta forest domain mod1, fig.width = 8, fig.height = 33, fig.show = 'hide', results = 'hide', warning = FALSE, message = FALSE}
meta::forest(domain_subgroup_mod1,
             sortvar = TE, #sort by effect size
             xlim = c(-1.5, 1.5),
             leftcols = "studlab",
             rightlabs = c("Hedges' g", "95% CI"),
             text.random = "Overall effect",
             text.overall.random = TRUE,
             overall.hetstat = FALSE,
             print.byvar = F, #this removed "potency =" and just left subgroup label
             smlab = "",
             hetstat = FALSE,
             test.overall = F,
             overall = F,
             prediction = F)
```

```{r meta forest domain 2 plots}
#individual cog plots
dat_study_domain_group1 <- dat_study_domain %>%
  filter(cog_domain_lezak == "Attention" | cog_domain_lezak =="Psychomotor Functioning" | cog_domain_lezak =="Concept Formation & Reasoning" | cog_domain_lezak =="Perception")
dat_study_domain_group2 <- dat_study_domain %>%
  filter(cog_domain_lezak == "Memory" | cog_domain_lezak =="Executive Function" | cog_domain_lezak =="Intelligence" | cog_domain_lezak =="Language")

meta_domain_group1 <- metagen(g,
                            st_err,
                            data = dat_study_domain_group1,
                            studlab = paste(author, year),
                            comb.fixed = F,
                            hakn = T,
                            comb.random = T,
                            method.tau = "PM", #use Paule-Mandel method
                            sm = "SMD") # says we want to calculate SMD
domain_subgroup_group1 <- update.meta(meta_domain_group1, 
                                      byvar=cog_domain_lezak, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
meta_domain_group2 <- metagen(g,
                              st_err,
                              data = dat_study_domain_group2,
                              studlab = paste(author, year),
                              comb.fixed = F,
                              hakn = T,
                              comb.random = T,
                              method.tau = "PM", #use Paule-Mandel method
                              sm = "SMD") # says we want to calculate SMD
domain_subgroup_group2 <- update.meta(meta_domain_group2, 
                                      byvar=cog_domain_lezak, 
                                      comb.random = TRUE, 
                                      comb.fixed = FALSE)
```

```{r meta forest domain group1, fig.width = 8, fig.height = 18, fig.show = 'hide', results = 'hide', warning = FALSE, message = FALSE}
tiff(file='fig6a_meta_forest_cog.tiff', width = 6, height = 17.25, units = "in", res = 600, compression = "lzw")
meta::forest(domain_subgroup_group1,
             sortvar = TE, #sort by effect size
             xlim = c(-1.5, 1.5),
             leftcols = "studlab",
             rightlabs = c("Hedges' g", "95% CI"),
             text.random = "Overall effect",
             text.overall.random = TRUE,
             overall.hetstat = FALSE,
             print.byvar = F, #this removed "potency =" and just left subgroup label
             smlab = "",
             hetstat = FALSE,
             test.overall = F,
             overall = F,
             prediction = F)
dev.off()
```

```{r meta forest domain group2, fig.width = 8, fig.height = 18, fig.show = 'hide', results = 'hide', warning = FALSE, message = FALSE}
tiff(file='fig6b_meta_forest_cog.tiff', width = 6, height = 17.25, units = "in", res = 600, compression = "lzw")
meta::forest(domain_subgroup_group2,
             sortvar = TE, #sort by effect size
             xlim = c(-1.5, 1.5),
             leftcols = "studlab",
             rightlabs = c("Hedges' g", "95% CI"),
             text.random = "Overall effect",
             text.overall.random = TRUE,
             overall.hetstat = FALSE,
             print.byvar = F, #this removed "potency =" and just left subgroup label
             smlab = "",
             hetstat = FALSE,
             test.overall = F,
             overall = F,
             prediction = F)
dev.off()
```

Now, combine the two cognition plots into a single plot:
```{r meta forest domain combine, fig.show = 'hide', results = 'hide', warning = FALSE, message = FALSE}
library(multipanelfigure)
figure1 <- multi_panel_figure(width = 12, height = 17.25, unit = "in", columns = 2, rows = 1, row_spacing = 0) %>%
  fill_panel("fig6a_meta_forest_cog.tiff", column = 1) %>%
  fill_panel("fig6b_meta_forest_cog.tiff", column = 2)
tiff(file='fig6_meta_forest_cog.tiff', width = 12, height = 17.25, units = "in", res = 600, compression = "lzw")
figure1
dev.off()
```
____

##### *Drug class*

Create data set (`dat_study_class`) which has the average effect size by drug class within each study.

Drug class was defined by ATC group into:

* Urological
* Opioid analgesic
* Antiepileptic
* Antiparkinson
* Antipsychotic
* Antidepressant
* Respiratory

```{r class average}
dat_study_class <- dat %>%
  group_by(study, drug_class) %>% #group by study and drug class within studies
  mutate(g = mean(g, na.rm = T),
         st_err = mean(st_err, na.rm = T)) %>% #obtain average g and st err within each study/domain
  filter(row_number()==1) %>% #make each study/domain only appear on one row
  select(study, author, year, drug_class, g, st_err) #select relevant data
```

Then, run random effects model by subgroup (drug class):

* Use the Paule-Mandel method to estimate tau

```{r meta class mod1, results = 'hide'}
meta_class_mod1 <- metagen(g,
                    st_err,
                    data = dat_study_class,
                    studlab = paste(author, year),
                    comb.fixed = F,
                    hakn = T,
                    comb.random = T,
                    method.tau = "PM", #use Paule-Mandel method
                    sm = "SMD") # says we want to calculate SMD
class_subgroup_mod1 <- update.meta(meta_class_mod1, 
                                byvar=drug_class, 
                                comb.random = TRUE, 
                                comb.fixed = FALSE)
```

Forest plot:
```{r meta forest class mod1, fig.width = 8, fig.height = 14, results = 'hide', warning = FALSE, message = FALSE}
tiff(file='fig3_meta_forest_class.tiff', width = 6, height = 14.5, units = "in", res = 600, compression = "lzw")
meta::forest(class_subgroup_mod1,
             sortvar = TE, #sort by effect size
             xlim = c(-1.5, 1.5),
             leftcols = "studlab",
             rightlabs = c("Hedges' g", "95% CI"),
             text.random = "Overall effect",
             text.overall.random = TRUE,
             overall.hetstat = FALSE,
             print.byvar = F, #this removed "potency =" and just left subgroup label
             smlab = "",
             hetstat = FALSE,
             test.overall = F,
             overall = F,
             prediction = F)
dev.off()
```

_____

##### *Length of administration*

Create data set (`dat_study_duration`) which has the average effect size by length of administration within each study.

Length of administration was categorised as 3 groups:

* Current administration <=1 month (Acute)
* Current administration >1 month (Long-term)
* Historical administration (Historical)

```{r duration average}
dat_study_duration <- dat %>%
  group_by(study, duration) %>% #group by study and drug class within studies
  mutate(g = mean(g, na.rm = T),
         st_err = mean(st_err, na.rm = T)) %>% #obtain average g and st err within each study/domain
  filter(row_number()==1) %>% #make each study/domain only appear on one row
  select(study, author, year, duration, g, st_err) #select relevant data
```

Then, run random effects model by subgroup (duration):

* Use the Paule-Mandel method to estimate tau

```{r meta duration mod1, results = 'hide'}
meta_duration_mod1 <- metagen(g,
                    st_err,
                    data = dat_study_duration,
                    studlab = paste(author, year),
                    comb.fixed = F,
                    hakn = T,
                    comb.random = T,
                    method.tau = "PM", #use Paule-Mandel method
                    prediction = T, #True = print prediction interval for future studies based on present evidence
                    sm = "SMD") # says we want to calculate SMD
duration_subgroup_mod1 <- update.meta(meta_duration_mod1, 
                                byvar=duration, 
                                comb.random = TRUE, 
                                comb.fixed = FALSE)
```

Forest plot:
```{r meta forest duration mod1, fig.width = 8, fig.height = 13, results = 'hide', warning = FALSE, message = FALSE}
tiff(file='fig5_meta_forest_duration.tiff', width = 6, height = 13, units = "in", res = 600, compression = "lzw")
meta::forest(duration_subgroup_mod1,
             sortvar = TE, #sort by effect size
             xlim = c(-1.5, 1.5),
             leftcols = "studlab",
             rightlabs = c("Hedges' g", "95% CI"),
             text.random = "Overall effect",
             text.overall.random = TRUE,
             overall.hetstat = FALSE,
             print.byvar = F, #this removed "potency =" and just left subgroup label
             smlab = "",
             hetstat = FALSE,
             test.overall = F,
             prediction = F,
             overall = F)
dev.off()
```

____

### Assess publication bias
Steps:

1. Visually inspect funnel plots (effect size vs standard error) for bias
2. **If 10 or more studies**, use Egger's Test to test for small-study effect
    + If statistically significant asymmetry found (1-sided P<0.1), use Duval and Tweedie's Trim and Fill method to quantify magnitude of bias
3. **If <10 studies**, locate outliers in funnel plot and recalculate effect sizes after their removal

To run Egger's, load Egger's function (found [here](https://raw.githubusercontent.com/MathiasHarrer/dmetar/master/R/eggers.test.R))
```{r eggers, include = FALSE}
#' Perform Egger's test of the intercept
#'
#' This function performs Egger's test of the intercept for funnel plot asymmetry using an object
#' of class \code{meta}.
#'
#' @usage eggers.test(x)
#'
#' @param x An object of class \code{meta}, generated by the \code{metabin}, \code{metagen},
#' \code{metacont}, \code{metacor}, \code{metainc}, or \code{metaprop} function.
#'
#' @details Performs Egger's test (Egger et al., 1997) for funnel plot asymmetry.
#' The \code{\link[meta]{metabias}} function is called internally. Egger's test may lack
#' the statistical power to detect bias when the number of studies is small. Sterne et al.
#' (2011) recommend to perform funnel plot asymmetry tests only when \eqn{k \geq 10}. A warning
#' is therefore printed when the number of studies in the \code{meta} object is \eqn{k < 10}.
#'
#' @references
#'
#' Harrer, M., Cuijpers, P., Furukawa, T.A, & Ebert, D. D. (2019).
#' \emph{Doing Meta-Analysis in R: A Hands-on Guide}. DOI: 10.5281/zenodo.2551803. \href{https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/smallstudyeffects.html}{Chapter 9.1}
#'
#' Egger M, Smith GD, Schneider M & Minder C (1997), Bias in meta-analysis detected by a simple,
#' graphical test. \emph{BMJ}, 315, 629–634.
#'
#' Sterne, JAC et al. (2011), Recommendations for Examining and Interpreting Funnel Plot
#' Asymmetry in Meta-Analyses of Randomised Controlled Trials. \emph{BMJ}
#' 343, 1, doi: 10.1136/bmj.d4002 .
#'
#' @author Mathias Harrer & David Daniel Ebert
#'
#' @importFrom meta metabias
#' @importFrom graphics abline axis lines mtext par plot points rect segments text
#' @importFrom stats as.formula hat influence ks.test optimize pbinom pchisq pf pnorm pt punif qchisq qf qnorm qt reformulate reorder setNames uniroot
#'
#' @return Returns a data.frame containing the following columns:
#' \itemize{
#' \item \code{Intercept}: The intercept (bias).
#' \item \code{ConfidenceInterval}: The 95\% confidence interval of the intercept.
#' \item \code{t}: The t-statistic for the intercept test.
#' \item \code{p}: The \eqn{p}-value for Egger's test.
#' }
#'
#' @export eggers.test
#'
#' @seealso \code{\link[meta]{metabias}}
#'
#' @examples
#' # Create meta-analysis results using the 'metagen' function
#' suppressPackageStartupMessages(library(meta))
#' data(ThirdWave)
#' m = metagen(TE, seTE, studlab = paste(Author),
#'     data = ThirdWave, comb.random = FALSE, hakn=TRUE)
#'
#' # Plug result into 'eggers.test' function
#' eggers.test(m)


eggers.test = function(x) {

    # Validate
    x = x

    if (x$k < 10) {

        warning(paste("Your meta-analysis contains k =", x$k, "studies. Egger's test may lack the statistical power to detect bias when the number of studies is small (i.e., k<10)."))

    }

    if (class(x)[1] %in% c("meta", "metabin", "metagen", "metacont", "metacor", "metainc", "metaprop")) {

        # Conduct metabias
        eggers = meta::metabias(x, k.min = 3, method = "linreg")

        # Get Intercept
        intercept = as.numeric(eggers$estimate[1]) %>% round(digits = 3)

        # Get SE
        se = as.numeric(eggers$estimate[2])

        # Calculate 95CI
        LLCI = intercept - 1.96 * se %>% round(digits = 1)
        ULCI = intercept + 1.96 * se %>% round(digits = 1)
        CI = paste(LLCI, "-", ULCI, sep = "")

        # Get t
        t = as.numeric(eggers$statistic) %>% round(digits = 3)

        # Get df
        df = as.numeric(eggers$parameters)

        # Get p
        p = as.numeric(eggers$p.value) %>% round(digits = 5)

        # Make df
        df = data.frame(Intercept = intercept, ConfidenceInterval = CI, t = t, p = p)
        row.names(df) = "Egger's test"

    } else {

        stop("x must be of type 'metabin', 'metagen', 'metacont', 'metainc' or 'metaprop'")

    }

    return(df)

}


```

____

#### Whole meta-analysis
```{r meta funnel whole, results = 'hide', warning = FALSE, message = FALSE}
png(file='figS1_meta_funnel_whole_1.png', width = 8, height = 6, units = "in", res = 300)
funnel.meta(meta_all_mod1, xlab = "Hedges' g")
dev.off()
```

```{r meta eggers whole}
eggers_whole <- eggers.test(x = meta_all_mod1)
eggers_whole
```

p>0.1, so no further action required.

____

### Results

**Whole analysis**

k | g | LL | UL | p | tau^2^ | I^2^ | Q
---- | ---- | ---- | ---- | ---- | ---- | ---- | ----
`r meta_all_mod1[["k"]]` |`r meta_all_mod1[["TE.random"]]` |`r meta_all_mod1[["lower.random"]]` | `r meta_all_mod1[["upper.random"]]` | `r meta_all_mod1[["pval.random"]]` | `r meta_all_mod1[["tau2"]]` | `r meta_all_mod1[["I2"]]*100`% | `r meta_all_mod1[["Q"]]`

**Sub-analysis table (combining with random-effects)**


Sub-analysis | k | g | 95% CI | p | tau^2^ | I^2^ | Q
---- | ---- | ---- | ---- | ---- | ---- | ---- | ---- 
`r class_subgroup_mod1[["bylevs"]][[1]]` | `r class_subgroup_mod1[["k.w"]][[1]]` | `r class_subgroup_mod1[["TE.random.w"]][[1]]` | `r class_subgroup_mod1[["lower.random.w"]][[1]]` - `r class_subgroup_mod1[["upper.random.w"]][[1]]` | `r class_subgroup_mod1[["pval.random.w"]][[1]]` | `r class_subgroup_mod1[["tau2.w"]][[1]]` | `r class_subgroup_mod1[["I2.w"]][[1]]*100` | `r class_subgroup_mod1[["Q.w"]][[1]]` 
`r class_subgroup_mod1[["bylevs"]][[2]]` | `r class_subgroup_mod1[["k.w"]][[2]]` | `r class_subgroup_mod1[["TE.random.w"]][[2]]` | `r class_subgroup_mod1[["lower.random.w"]][[2]]` - `r class_subgroup_mod1[["upper.random.w"]][[2]]` | `r class_subgroup_mod1[["pval.random.w"]][[2]]` | `r class_subgroup_mod1[["tau2.w"]][[2]]` | `r class_subgroup_mod1[["I2.w"]][[2]]*100` | `r class_subgroup_mod1[["Q.w"]][[2]]` 
`r class_subgroup_mod1[["bylevs"]][[3]]` | `r class_subgroup_mod1[["k.w"]][[3]]` | `r class_subgroup_mod1[["TE.random.w"]][[3]]` | `r class_subgroup_mod1[["lower.random.w"]][[3]]` - `r class_subgroup_mod1[["upper.random.w"]][[3]]` | `r class_subgroup_mod1[["pval.random.w"]][[3]]` | `r class_subgroup_mod1[["tau2.w"]][[3]]` | `r class_subgroup_mod1[["I2.w"]][[3]]*100` | `r class_subgroup_mod1[["Q.w"]][[3]]` 
`r class_subgroup_mod1[["bylevs"]][[4]]` | `r class_subgroup_mod1[["k.w"]][[4]]` | `r class_subgroup_mod1[["TE.random.w"]][[4]]` | `r class_subgroup_mod1[["lower.random.w"]][[4]]` - `r class_subgroup_mod1[["upper.random.w"]][[4]]` | `r class_subgroup_mod1[["pval.random.w"]][[4]]` | `r class_subgroup_mod1[["tau2.w"]][[4]]` | `r class_subgroup_mod1[["I2.w"]][[4]]*100` | `r class_subgroup_mod1[["Q.w"]][[4]]` 
`r class_subgroup_mod1[["bylevs"]][[5]]` | `r class_subgroup_mod1[["k.w"]][[5]]` | `r class_subgroup_mod1[["TE.random.w"]][[5]]` | `r class_subgroup_mod1[["lower.random.w"]][[5]]` - `r class_subgroup_mod1[["upper.random.w"]][[5]]` | `r class_subgroup_mod1[["pval.random.w"]][[5]]` | `r class_subgroup_mod1[["tau2.w"]][[5]]` | `r class_subgroup_mod1[["I2.w"]][[5]]*100`  | `r class_subgroup_mod1[["Q.w"]][[5]]` 
`r class_subgroup_mod1[["bylevs"]][[6]]` | `r class_subgroup_mod1[["k.w"]][[6]]` | `r class_subgroup_mod1[["TE.random.w"]][[6]]` | `r class_subgroup_mod1[["lower.random.w"]][[6]]` - `r class_subgroup_mod1[["upper.random.w"]][[6]]` | `r class_subgroup_mod1[["pval.random.w"]][[6]]` | `r class_subgroup_mod1[["tau2.w"]][[6]]` | `r class_subgroup_mod1[["I2.w"]][[6]]*100` | `r class_subgroup_mod1[["Q.w"]][[6]]` 
`r class_subgroup_mod1[["bylevs"]][[7]]` | `r class_subgroup_mod1[["k.w"]][[7]]` | `r class_subgroup_mod1[["TE.random.w"]][[7]]` | `r class_subgroup_mod1[["lower.random.w"]][[7]]` - `r class_subgroup_mod1[["upper.random.w"]][[7]]` | `r class_subgroup_mod1[["pval.random.w"]][[7]]` | `r class_subgroup_mod1[["tau2.w"]][[7]]` | `r class_subgroup_mod1[["I2.w"]][[7]]*100` | `r class_subgroup_mod1[["Q.w"]][[7]]` 
`r potency_subgroup_mod1[["bylevs"]][[1]]` | `r potency_subgroup_mod1[["k.w"]][[1]]` | `r potency_subgroup_mod1[["TE.random.w"]][[1]]` | `r potency_subgroup_mod1[["lower.random.w"]][[1]]` - `r potency_subgroup_mod1[["upper.random.w"]][[1]]` | `r potency_subgroup_mod1[["pval.random.w"]][[1]]` | `r potency_subgroup_mod1[["tau2.w"]][[1]]` | `r potency_subgroup_mod1[["I2.w"]][[1]]*100` | `r potency_subgroup_mod1[["Q.w"]][[1]]`
`r potency_subgroup_mod1[["bylevs"]][[2]]` | `r potency_subgroup_mod1[["k.w"]][[2]]` | `r potency_subgroup_mod1[["TE.random.w"]][[2]]` | `r potency_subgroup_mod1[["lower.random.w"]][[2]]` - `r potency_subgroup_mod1[["upper.random.w"]][[2]]` | `r potency_subgroup_mod1[["pval.random.w"]][[2]]` | `r potency_subgroup_mod1[["tau2.w"]][[2]]` | `r potency_subgroup_mod1[["I2.w"]][[2]]*100` | `r potency_subgroup_mod1[["Q.w"]][[2]]`
`r duration_subgroup_mod1[["bylevs"]][[1]]` | `r duration_subgroup_mod1[["k.w"]][[1]]` | `r duration_subgroup_mod1[["TE.random.w"]][[1]]` | `r duration_subgroup_mod1[["lower.random.w"]][[1]]` - `r duration_subgroup_mod1[["upper.random.w"]][[1]]` | `r duration_subgroup_mod1[["pval.random.w"]][[1]]` | `r duration_subgroup_mod1[["tau2.w"]][[1]]` | `r duration_subgroup_mod1[["I2.w"]][[1]]*100` | `r duration_subgroup_mod1[["Q.w"]][[1]]`
`r duration_subgroup_mod1[["bylevs"]][[2]]` | `r duration_subgroup_mod1[["k.w"]][[2]]` | `r duration_subgroup_mod1[["TE.random.w"]][[2]]` | `r duration_subgroup_mod1[["lower.random.w"]][[2]]` - `r duration_subgroup_mod1[["upper.random.w"]][[2]]` | `r duration_subgroup_mod1[["pval.random.w"]][[2]]` | `r duration_subgroup_mod1[["tau2.w"]][[2]]` | `r duration_subgroup_mod1[["I2.w"]][[2]]*100` | `r duration_subgroup_mod1[["Q.w"]][[2]]`
`r duration_subgroup_mod1[["bylevs"]][[3]]` | `r duration_subgroup_mod1[["k.w"]][[3]]` | `r duration_subgroup_mod1[["TE.random.w"]][[3]]` | `r duration_subgroup_mod1[["lower.random.w"]][[3]]` - `r duration_subgroup_mod1[["upper.random.w"]][[3]]` | `r duration_subgroup_mod1[["pval.random.w"]][[3]]` | `r duration_subgroup_mod1[["tau2.w"]][[3]]` | `r duration_subgroup_mod1[["I2.w"]][[3]]*100` | `r duration_subgroup_mod1[["Q.w"]][[3]]`
`r domain_subgroup_mod1[["bylevs"]][[1]]` | `r domain_subgroup_mod1[["k.w"]][[1]]` | `r domain_subgroup_mod1[["TE.random.w"]][[1]]` | `r domain_subgroup_mod1[["lower.random.w"]][[1]]` - `r domain_subgroup_mod1[["upper.random.w"]][[1]]` | `r domain_subgroup_mod1[["pval.random.w"]][[1]]` | `r domain_subgroup_mod1[["tau2.w"]][[1]]` | `r domain_subgroup_mod1[["I2.w"]][[1]]*100` | `r domain_subgroup_mod1[["Q.w"]][[1]]`
`r domain_subgroup_mod1[["bylevs"]][[2]]` | `r domain_subgroup_mod1[["k.w"]][[2]]` | `r domain_subgroup_mod1[["TE.random.w"]][[2]]` | `r domain_subgroup_mod1[["lower.random.w"]][[2]]` - `r domain_subgroup_mod1[["upper.random.w"]][[2]]` | `r domain_subgroup_mod1[["pval.random.w"]][[2]]` | `r domain_subgroup_mod1[["tau2.w"]][[2]]` | `r domain_subgroup_mod1[["I2.w"]][[2]]*100` | `r domain_subgroup_mod1[["Q.w"]][[2]]`
`r domain_subgroup_mod1[["bylevs"]][[3]]` | `r domain_subgroup_mod1[["k.w"]][[3]]` | `r domain_subgroup_mod1[["TE.random.w"]][[3]]` | `r domain_subgroup_mod1[["lower.random.w"]][[3]]` - `r domain_subgroup_mod1[["upper.random.w"]][[3]]` | `r domain_subgroup_mod1[["pval.random.w"]][[3]]` | `r domain_subgroup_mod1[["tau2.w"]][[3]]` | `r domain_subgroup_mod1[["I2.w"]][[3]]*100` | `r domain_subgroup_mod1[["Q.w"]][[3]]`
`r domain_subgroup_mod1[["bylevs"]][[4]]` | `r domain_subgroup_mod1[["k.w"]][[4]]` | `r domain_subgroup_mod1[["TE.random.w"]][[4]]` | `r domain_subgroup_mod1[["lower.random.w"]][[4]]` - `r domain_subgroup_mod1[["upper.random.w"]][[4]]` | `r domain_subgroup_mod1[["pval.random.w"]][[4]]` | `r domain_subgroup_mod1[["tau2.w"]][[4]]` | `r domain_subgroup_mod1[["I2.w"]][[4]]*100` | `r domain_subgroup_mod1[["Q.w"]][[4]]`
`r domain_subgroup_mod1[["bylevs"]][[5]]` | `r domain_subgroup_mod1[["k.w"]][[5]]` | `r domain_subgroup_mod1[["TE.random.w"]][[5]]` | `r domain_subgroup_mod1[["lower.random.w"]][[5]]` - `r domain_subgroup_mod1[["upper.random.w"]][[5]]` | `r domain_subgroup_mod1[["pval.random.w"]][[5]]` | `r domain_subgroup_mod1[["tau2.w"]][[5]]` | `r domain_subgroup_mod1[["I2.w"]][[5]]*100` | `r domain_subgroup_mod1[["Q.w"]][[5]]`
`r domain_subgroup_mod1[["bylevs"]][[6]]` | `r domain_subgroup_mod1[["k.w"]][[6]]` | `r domain_subgroup_mod1[["TE.random.w"]][[6]]` | `r domain_subgroup_mod1[["lower.random.w"]][[6]]` - `r domain_subgroup_mod1[["upper.random.w"]][[6]]` | `r domain_subgroup_mod1[["pval.random.w"]][[6]]` | `r domain_subgroup_mod1[["tau2.w"]][[6]]` | `r domain_subgroup_mod1[["I2.w"]][[6]]*100` | `r domain_subgroup_mod1[["Q.w"]][[6]]`
`r domain_subgroup_mod1[["bylevs"]][[7]]` | `r domain_subgroup_mod1[["k.w"]][[7]]` | `r domain_subgroup_mod1[["TE.random.w"]][[7]]` | `r domain_subgroup_mod1[["lower.random.w"]][[7]]` - `r domain_subgroup_mod1[["upper.random.w"]][[7]]` | `r domain_subgroup_mod1[["pval.random.w"]][[7]]` | `r domain_subgroup_mod1[["tau2.w"]][[7]]` | `r domain_subgroup_mod1[["I2.w"]][[7]]*100` | `r domain_subgroup_mod1[["Q.w"]][[7]]`
`r domain_subgroup_mod1[["bylevs"]][[8]]` | `r domain_subgroup_mod1[["k.w"]][[8]]` | `r domain_subgroup_mod1[["TE.random.w"]][[8]]` | `r domain_subgroup_mod1[["lower.random.w"]][[8]]` - `r domain_subgroup_mod1[["upper.random.w"]][[8]]` | `r domain_subgroup_mod1[["pval.random.w"]][[8]]` | `r domain_subgroup_mod1[["tau2.w"]][[8]]` | `r domain_subgroup_mod1[["I2.w"]][[8]]*100` | `r domain_subgroup_mod1[["Q.w"]][[8]]`

**Sub-analysis table (combining with fixed-effects)**


Sub-analysis | k | g | 95% CI | p | tau^2^ | I^2^ | Q
---- | ---- | ---- | ---- | ---- | ---- | ---- | ---- 
`r class_subgroup_mod1[["bylevs"]][[1]]` | `r class_subgroup_mod1[["k.w"]][[1]]` | `r class_subgroup_mod1[["TE.fixed.w"]][[1]]` | `r class_subgroup_mod1[["lower.fixed.w"]][[1]]` - `r class_subgroup_mod1[["upper.fixed.w"]][[1]]` | `r class_subgroup_mod1[["pval.fixed.w"]][[1]]` | `r class_subgroup_mod1[["tau2.w"]][[1]]` | `r class_subgroup_mod1[["I2.w"]][[1]]*100` | `r class_subgroup_mod1[["Q.w"]][[1]]` 
`r class_subgroup_mod1[["bylevs"]][[2]]` | `r class_subgroup_mod1[["k.w"]][[2]]` | `r class_subgroup_mod1[["TE.fixed.w"]][[2]]` | `r class_subgroup_mod1[["lower.fixed.w"]][[2]]` - `r class_subgroup_mod1[["upper.fixed.w"]][[2]]` | `r class_subgroup_mod1[["pval.fixed.w"]][[2]]` | `r class_subgroup_mod1[["tau2.w"]][[2]]` | `r class_subgroup_mod1[["I2.w"]][[2]]*100` | `r class_subgroup_mod1[["Q.w"]][[2]]` 
`r class_subgroup_mod1[["bylevs"]][[3]]` | `r class_subgroup_mod1[["k.w"]][[3]]` | `r class_subgroup_mod1[["TE.fixed.w"]][[3]]` | `r class_subgroup_mod1[["lower.fixed.w"]][[3]]` - `r class_subgroup_mod1[["upper.fixed.w"]][[3]]` | `r class_subgroup_mod1[["pval.fixed.w"]][[3]]` | `r class_subgroup_mod1[["tau2.w"]][[3]]` | `r class_subgroup_mod1[["I2.w"]][[3]]*100` | `r class_subgroup_mod1[["Q.w"]][[3]]` 
`r class_subgroup_mod1[["bylevs"]][[4]]` | `r class_subgroup_mod1[["k.w"]][[4]]` | `r class_subgroup_mod1[["TE.fixed.w"]][[4]]` | `r class_subgroup_mod1[["lower.fixed.w"]][[4]]` - `r class_subgroup_mod1[["upper.fixed.w"]][[4]]` | `r class_subgroup_mod1[["pval.fixed.w"]][[4]]` | `r class_subgroup_mod1[["tau2.w"]][[4]]` | `r class_subgroup_mod1[["I2.w"]][[4]]*100` | `r class_subgroup_mod1[["Q.w"]][[4]]` 
`r class_subgroup_mod1[["bylevs"]][[5]]` | `r class_subgroup_mod1[["k.w"]][[5]]` | `r class_subgroup_mod1[["TE.fixed.w"]][[5]]` | `r class_subgroup_mod1[["lower.fixed.w"]][[5]]` - `r class_subgroup_mod1[["upper.fixed.w"]][[5]]` | `r class_subgroup_mod1[["pval.fixed.w"]][[5]]` | `r class_subgroup_mod1[["tau2.w"]][[5]]` | `r class_subgroup_mod1[["I2.w"]][[5]]*100`  | `r class_subgroup_mod1[["Q.w"]][[5]]` 
`r class_subgroup_mod1[["bylevs"]][[6]]` | `r class_subgroup_mod1[["k.w"]][[6]]` | `r class_subgroup_mod1[["TE.fixed.w"]][[6]]` | `r class_subgroup_mod1[["lower.fixed.w"]][[6]]` - `r class_subgroup_mod1[["upper.fixed.w"]][[6]]` | `r class_subgroup_mod1[["pval.fixed.w"]][[6]]` | `r class_subgroup_mod1[["tau2.w"]][[6]]` | `r class_subgroup_mod1[["I2.w"]][[6]]*100` | `r class_subgroup_mod1[["Q.w"]][[6]]` 
`r class_subgroup_mod1[["bylevs"]][[7]]` | `r class_subgroup_mod1[["k.w"]][[7]]` | `r class_subgroup_mod1[["TE.fixed.w"]][[7]]` | `r class_subgroup_mod1[["lower.fixed.w"]][[7]]` - `r class_subgroup_mod1[["upper.fixed.w"]][[7]]` | `r class_subgroup_mod1[["pval.fixed.w"]][[7]]` | `r class_subgroup_mod1[["tau2.w"]][[7]]` | `r class_subgroup_mod1[["I2.w"]][[7]]*100` | `r class_subgroup_mod1[["Q.w"]][[7]]` 
`r potency_subgroup_mod1[["bylevs"]][[1]]` | `r potency_subgroup_mod1[["k.w"]][[1]]` | `r potency_subgroup_mod1[["TE.fixed.w"]][[1]]` | `r potency_subgroup_mod1[["lower.fixed.w"]][[1]]` - `r potency_subgroup_mod1[["upper.fixed.w"]][[1]]` | `r potency_subgroup_mod1[["pval.fixed.w"]][[1]]` | `r potency_subgroup_mod1[["tau2.w"]][[1]]` | `r potency_subgroup_mod1[["I2.w"]][[1]]*100` | `r potency_subgroup_mod1[["Q.w"]][[1]]`
`r potency_subgroup_mod1[["bylevs"]][[2]]` | `r potency_subgroup_mod1[["k.w"]][[2]]` | `r potency_subgroup_mod1[["TE.fixed.w"]][[2]]` | `r potency_subgroup_mod1[["lower.fixed.w"]][[2]]` - `r potency_subgroup_mod1[["upper.fixed.w"]][[2]]` | `r potency_subgroup_mod1[["pval.fixed.w"]][[2]]` | `r potency_subgroup_mod1[["tau2.w"]][[2]]` | `r potency_subgroup_mod1[["I2.w"]][[2]]*100` | `r potency_subgroup_mod1[["Q.w"]][[2]]`
`r duration_subgroup_mod1[["bylevs"]][[1]]` | `r duration_subgroup_mod1[["k.w"]][[1]]` | `r duration_subgroup_mod1[["TE.fixed.w"]][[1]]` | `r duration_subgroup_mod1[["lower.fixed.w"]][[1]]` - `r duration_subgroup_mod1[["upper.fixed.w"]][[1]]` | `r duration_subgroup_mod1[["pval.fixed.w"]][[1]]` | `r duration_subgroup_mod1[["tau2.w"]][[1]]` | `r duration_subgroup_mod1[["I2.w"]][[1]]*100` | `r duration_subgroup_mod1[["Q.w"]][[1]]`
`r duration_subgroup_mod1[["bylevs"]][[2]]` | `r duration_subgroup_mod1[["k.w"]][[2]]` | `r duration_subgroup_mod1[["TE.fixed.w"]][[2]]` | `r duration_subgroup_mod1[["lower.fixed.w"]][[2]]` - `r duration_subgroup_mod1[["upper.fixed.w"]][[2]]` | `r duration_subgroup_mod1[["pval.fixed.w"]][[2]]` | `r duration_subgroup_mod1[["tau2.w"]][[2]]` | `r duration_subgroup_mod1[["I2.w"]][[2]]*100` | `r duration_subgroup_mod1[["Q.w"]][[2]]`
`r duration_subgroup_mod1[["bylevs"]][[3]]` | `r duration_subgroup_mod1[["k.w"]][[3]]` | `r duration_subgroup_mod1[["TE.fixed.w"]][[3]]` | `r duration_subgroup_mod1[["lower.fixed.w"]][[3]]` - `r duration_subgroup_mod1[["upper.fixed.w"]][[3]]` | `r duration_subgroup_mod1[["pval.fixed.w"]][[3]]` | `r duration_subgroup_mod1[["tau2.w"]][[3]]` | `r duration_subgroup_mod1[["I2.w"]][[3]]*100` | `r duration_subgroup_mod1[["Q.w"]][[3]]`
`r domain_subgroup_mod1[["bylevs"]][[1]]` | `r domain_subgroup_mod1[["k.w"]][[1]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[1]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[1]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[1]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[1]]` | `r domain_subgroup_mod1[["tau2.w"]][[1]]` | `r domain_subgroup_mod1[["I2.w"]][[1]]*100` | `r domain_subgroup_mod1[["Q.w"]][[1]]`
`r domain_subgroup_mod1[["bylevs"]][[2]]` | `r domain_subgroup_mod1[["k.w"]][[2]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[2]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[2]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[2]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[2]]` | `r domain_subgroup_mod1[["tau2.w"]][[2]]` | `r domain_subgroup_mod1[["I2.w"]][[2]]*100` | `r domain_subgroup_mod1[["Q.w"]][[2]]`
`r domain_subgroup_mod1[["bylevs"]][[3]]` | `r domain_subgroup_mod1[["k.w"]][[3]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[3]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[3]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[3]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[3]]` | `r domain_subgroup_mod1[["tau2.w"]][[3]]` | `r domain_subgroup_mod1[["I2.w"]][[3]]*100` | `r domain_subgroup_mod1[["Q.w"]][[3]]`
`r domain_subgroup_mod1[["bylevs"]][[4]]` | `r domain_subgroup_mod1[["k.w"]][[4]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[4]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[4]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[4]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[4]]` | `r domain_subgroup_mod1[["tau2.w"]][[4]]` | `r domain_subgroup_mod1[["I2.w"]][[4]]*100` | `r domain_subgroup_mod1[["Q.w"]][[4]]`
`r domain_subgroup_mod1[["bylevs"]][[5]]` | `r domain_subgroup_mod1[["k.w"]][[5]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[5]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[5]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[5]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[5]]` | `r domain_subgroup_mod1[["tau2.w"]][[5]]` | `r domain_subgroup_mod1[["I2.w"]][[5]]*100` | `r domain_subgroup_mod1[["Q.w"]][[5]]`
`r domain_subgroup_mod1[["bylevs"]][[6]]` | `r domain_subgroup_mod1[["k.w"]][[6]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[6]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[6]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[6]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[6]]` | `r domain_subgroup_mod1[["tau2.w"]][[6]]` | `r domain_subgroup_mod1[["I2.w"]][[6]]*100` | `r domain_subgroup_mod1[["Q.w"]][[6]]`
`r domain_subgroup_mod1[["bylevs"]][[7]]` | `r domain_subgroup_mod1[["k.w"]][[7]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[7]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[7]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[7]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[7]]` | `r domain_subgroup_mod1[["tau2.w"]][[7]]` | `r domain_subgroup_mod1[["I2.w"]][[7]]*100` | `r domain_subgroup_mod1[["Q.w"]][[7]]`
`r domain_subgroup_mod1[["bylevs"]][[8]]` | `r domain_subgroup_mod1[["k.w"]][[8]]` | `r domain_subgroup_mod1[["TE.fixed.w"]][[8]]` | `r domain_subgroup_mod1[["lower.fixed.w"]][[8]]` - `r domain_subgroup_mod1[["upper.fixed.w"]][[8]]` | `r domain_subgroup_mod1[["pval.fixed.w"]][[8]]` | `r domain_subgroup_mod1[["tau2.w"]][[8]]` | `r domain_subgroup_mod1[["I2.w"]][[8]]*100` | `r domain_subgroup_mod1[["Q.w"]][[8]]`


**Sub-analysis: Test of subgroup differences**

Sub-analysis | Q (random) | p (random) | Q (fixed) | p (fixed)
--- | --- | --- |  --- | ---
Class | `r class_subgroup_mod1[["Q.b.random"]]` | `r class_subgroup_mod1[["pval.Q.b.random"]]` | `r class_subgroup_mod1[["Q.b.fixed"]]` | `r class_subgroup_mod1[["pval.Q.b.fixed"]]` 
Potency | `r potency_subgroup_mod1[["Q.b.random"]]` | `r potency_subgroup_mod1[["pval.Q.b.random"]]` | `r potency_subgroup_mod1[["Q.b.fixed"]]` | `r potency_subgroup_mod1[["pval.Q.b.fixed"]]` 
Duration | `r duration_subgroup_mod1[["Q.b.random"]]` | `r duration_subgroup_mod1[["pval.Q.b.random"]]` | `r duration_subgroup_mod1[["Q.b.fixed"]]` | `r duration_subgroup_mod1[["pval.Q.b.fixed"]]` 
Domain | `r domain_subgroup_mod1[["Q.b.random"]]` | `r domain_subgroup_mod1[["pval.Q.b.random"]]` | `r domain_subgroup_mod1[["Q.b.fixed"]]` | `r domain_subgroup_mod1[["pval.Q.b.fixed"]]` 
